Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI~837: A Young Validated Planet in IC~2602

### 2020-07-27 paper/ms.tex
update manuscript

Over the first 100 million years of their lives, exoplanet systems are
expected to undergo major physical and dynamical changes.  For a
typical Sun-like star, the protoplanetary disk disperses within
roughly 1--10 million years
\citep{mamajek_initial_2009,fedele_timescale_2010,dullemond_inner_2010,williams_protoplanetary_2011}.
Gas giants presumably finish accreting before the end of disk
dispersal \citep{pollack_formation_1996}.  While rocky planets may
fully form within only a few million years
\citep{dauphas_hf-w-th_2011}, they can also undergo significant growth
over the next 10--100 million years through giant impacts \citep[{\it
e.g.},][]{kleine_hf-w_2009,konig_earths_2011,morbidelli_building_2012,raymond_terrestrial_2014}.
The Moon, for instance, may have formed from debris ejected during a
collision between the proto-Earth and a planetesimal during Earth's
first 100 million years \citep{cameron_origin_1976,canup_origin_2001}.

A number of other processes are expected to shape young exoplanets.
After accreting, planets with gaseous envelopes are thought to cool
and contract, and their atmospheres are expected to undergo
photoevaporation \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
The relative importance of contraction and photoevaporation is set by
the planetary mass, as well as the radiation environment.  The
effectiveness of photoevaporation can be inferred from observations of
planetary winds in the metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

Beyond physical changes, dynamical changes are expected in the
semi-major axes, eccentricities, and stellar obliquities of young
planets.  When the gas disk is present, the planetary semi-major axis
is thought to change in step with the viscous evolution of the disk
\citep{lin_orbital_1996}.  High-eccentricity migration processes
including planet-planet scattering, secular chaos, and Kozai-Lidov
oscillations can also occur \citep[{\it
e.g.},][]{chatterjee_dynamical_2008,lithwick_secular_2014,fabrycky_shrinking_2007}.
The circularization timescale is thought to be such that for any giant
planets that migrated early, their orbits should circularize within
100 million years \citep{zahn_tidal_1977}.

@@

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.

@@

With the aim of advancing the young planet census, we have been using
data from the TESS spacecraft \citep{ricker_transiting_2015} to
perform a Cluster Difference Imaging Photometric Survey
\citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
candidate young stars that have been reported in the literature.  At
the time of writing, we had made $\sim$$6\times10^5$ light curves from
the first year of TESS observations. The light curves are available at
MAST\footnote{\stscilink, and see \datasetlink}.  Searching through a
subset of these light curves brought our attention to the candidate
transiting planet, \pn, that is the subject of this analysis.

>>>>

Over the first 100 million years of their lives, exoplanet systems are
expected to undergo major physical and dynamical changes.  For a
typical Sun-like star, the protoplanetary disk disperses within
roughly 1--10 million years
\citep{mamajek_initial_2009,fedele_timescale_2010,dullemond_inner_2010,williams_protoplanetary_2011}.
Gas giants presumably finish accreting before the end of disk
dispersal \citep{pollack_formation_1996}.  While rocky planets may
fully form within only a few million years
\citep{dauphas_hf-w-th_2011}, they can also undergo significant growth
over the next 10--100 million years through giant impacts \citep[{\it
e.g.},][]{kleine_hf-w_2009,konig_earths_2011,morbidelli_building_2012,raymond_terrestrial_2014}.
The Moon, for instance, may have formed from debris ejected during a
collision between the proto-Earth and a planetesimal during Earth's
first 100 million years \citep{cameron_origin_1976,canup_origin_2001,touboul_late_2007}.

A number of other processes are expected to shape young exoplanets.
After accreting, planets with gaseous envelopes are thought to cool
and contract, and their atmospheres are expected to undergo a mix of
photoevaporation and core-powered mass loss \citep[{\it
e.g.},][]{Fortney_et_al_2007,Owen_Wu_2013,Fulton_et_al_2017,gupta_sculpting_2019,gupta_signatures_2020}.
The relative importance of cooling and photoevaporation is set by the
planetary surface gravity, as well as the radiation environment.  The
timescale for core-powered mass loss may in some cases exceed the
$\sim$100 Myr during which photoevaporation is expected to be
effective \citep{ginzburg_superearth_2016,owen_evaporation_2017}.
Both processes could be directly observed through observations of
planetary winds in the metastable 1083$\,$nm He line
\citep{spake_helium_2018,oklopcic_new_2018,mansfield_detection_2018}.

Beyond physical changes, dynamical changes are expected in the
semi-major axes, eccentricities, and stellar obliquities of young
planets.  When the gas disk is present, the planetary semi-major axis
is thought to change in step with the viscous evolution of the disk
\citep{lin_orbital_1996}.  High-eccentricity migration processes
including planet-planet scattering, secular chaos, and Kozai-Lidov
oscillations can also occur \citep[{\it
e.g.},][]{fabrycky_shrinking_2007,chatterjee_dynamical_2008,lithwick_secular_2014}.
The circularization timescale is thought to be such that for any giant
planets that migrated early, their orbits should circularize within
100 million years \citep{zahn_tidal_1977}.

@@

A few dozen planets in clusters have been detected, and fewer still
have been closely characterized.  Despite the challenges of
starspot-induced radial velocity (RV) variations, RV surveys found
success in the Hyades, NGC~2523, Praesepe, and M~67
\citep{Sato_et_al_2007,lovis_mayor_2007,Quinn_et_al_2012,Malavolta_et_al_2016,brucalassi_search_2017}.
RV surveys of highly active pre-main sequence stars in Taurus also led
to the youngest hot Jupiters yet reported orbiting V830~Tau, TAP~26, and
CI~Tau
\citep{donati_hj_2016,johns-krull_candidate_2016,yu_hot_2017,biddle_k2_2018,flagg_co_2019}.
Follow-up by Damasso et al{.} (2020, submitted) did not detect
the planetary signal in V830~Tau.

@@

With the aim of advancing the young planet census, we have been using
data from the TESS spacecraft \citep{ricker_transiting_2015} to
perform a Cluster Difference Imaging Photometric Survey
\citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
candidate young stars that have been reported in the literature.  At
the time of writing, we had made $\sim$$6\times10^5$ light curves from
the first year of TESS observations. The light curves are available at
MAST\footnote{\stscilink}, and through \datasetlink.  Searching through a
subset of these light curves brought our attention to the candidate
transiting planet, \pn, that is the subject of this analysis.
